---
title: "Snowball Search and global quantification of the references"
format:
    html:
        toc: true
        toc-depth: 2
        embed-resources: true
        code-fold: true
        code-summary: "Show the code"
---

# Setup
```{r}
#| label: setup
#|

# library(bibtex)
library(openalexR)
library(writexl)
library(tibble)
library(dplyr)
library(ggplot2)
library(ggraph)
library(tidygraph)

library(knitr)

list.files(
    "R",
    full.names = TRUE,
    recursive = TRUE
) |>
    sapply(
        FUN <- source
    )


kp <- read.csv("./key_papers.csv")
kp <- split(kp, kp$ro)
```

# Searches

## OpenAlex

### Setup OpelAnex usage and do snowball serarch

```{r}
#| label: openalex_prep
#|

key_works <- lapply(
    kp,
    function(x) {
        oa_fetch(
            entity = "works",
            doi = x$doi,
            verbose = FALSE
        )
    }
)

saveRDS(key_works, "key_works.rds")

ids <- lapply(
    key_works,
    function(x){
        openalexR:::shorten_oaid(x$id)
    }
)

fn <- file.path(".", "data", "snowball.rds")
if (file.exists(fn)) {
    snowball <- readRDS(fn)
} else {
    snowball <- lapply(
        ids,
        function(x) {
            oa_snowball(
                identifier = x,
                verbose = FALSE
            )
        }
    )
    saveRDS(snowball, fn)
}

flat_snow <- lapply(
    snowball,
    function(x){
        snowball2df(x) |>
        as_tibble()
    }
)
```

### Save snowball as Excel file (`snowball_excel.xlsx`)

```{r}
#| label: openalex_excel
#|

###

lapply(
    names(snowball),
    function(x) {
        fn <- file.path(".", "data", paste0(x, ".xlsx"))
        to_xlsx(
            snowball = snowball[[x]], 
            flat_snow = flat_snow[[x]], 
            xls_filename = fn
        )    
    }
)
```

The column are: (the Concept columns are not that relevant at the moment)

- **id**: internal id fromOpenAlex
- **author**: authors of the paper
- **publication_year**: publication year
- **title**: title of the paper
- **doi**: doi of the paper
- **no_referenced_works**: number of references in the paper which are also in OpenAlex
- **cited_global**: Number of times the paper has been cited
- **cited_global_per_year**: standardised  number of times cirted (cited_global / number of years published)
- **no_connections**: number of connections in the rgaph, i.e. either cited or citing a paper in the snowball corpus
- **concepts_l0**: Concept 0. level assigned by OpenAlex
- **concepts_l1**: Concept 1. level assigned by OpenAlex
- **concepts_l2**: Concept 2. level assigned by OpenAlex
- **concepts_l3**: Concept 3. level assigned by OpenAlex
- **concepts_l4**: Concept 4. level assigned by OpenAlex
- **concepts_l5**: Concept 5. level assigned by OpenAlex
- **author_institute**: Institute of the authors
- **institute_country**: Country of the institute
- **abstract**: the abstract of the paper


### Graph of links between references

```{r}
#| label: openalex_graph
#|

lapply(
    names(snowball),
    function(x){
        plot_snowball(
            snowball[[x]],
            name = x
        )
    }
)
```

### Identification of references with more than one edge

This is the number of connections (`connection_count)`of the paper (`id`)

```{r}
#| label: openalex_edgecount
#|

mult_edge <- lapply(
    flat_snow,
    function(flat_snow) {
        mult_edge <- flat_snow |>
            select(id, connection_count) |>
            filter(connection_count > 1) |>
            arrange(desc(connection_count))
    }
)

links <- lapply(
    names(flat_snow),
    function(x) {
        flat_snow[[x]] |>
            filter(id %in% mult_edge[[x]]$id)
    }
)

lapply(
    links,
    function(links) {
        links |>
            select(id, display_name, publication_year, doi, connection_count) |>
            arrange(desc(connection_count)) |>
            knitr::kable()
    }
)
```



# Finalize
To convert to pdf run e.g.

```{bash}
#| eval: false
    wkhtmltopdf snowball.html snowball.pdf
```
